Forecasting biodiversity in breeding birds using best practices

### 2017-12-09 manuscript/reviewer_reply.Rmd

Dear XXX,
We would like to thank you and the two reviewers for the productive feedback on our manuscript. We have made minor revisions in clarifying our results, being more descriptive in our data and methods, and including more language on future directions of this research. More detailed responses to individual comments are described below.

Regards,

### 2017-12-09 manuscript/reviewer_reply.Rmd

>We have switched the panels and labeled them. Thank you for noticing this error.

*I will leave the remainder of the comments to the two reviewers.*

## Reviewer 1: Eric Ward
#### Basic reporting

*I found the paper very clear and easy to follow, with a good intro/discussion that tied the current work into previous studies. All data shared - in addition to code. More minor comments in General Comments section.*

*This question and forecasting competition was well designed. I had minor comments to improve clarity with models. The analysis is all documented/replicable on the Github repo. More minor comments in General Comments section.*

@@

>See comment above on using shorter time scale environmental variables.

*Line 124: I’m not as familiar with terrestrial projections, but are the CMIP5 projections relatively unbiased / precise when compared to recent data?*

>The accuracy of CMIP5 models varies by the variable considered. Temperature is represented very well over North America. Precipitation is challenging, especially over mountainous terrain, but the CMIP5 ensemble represents precipitation across North America relatively well ("Evaluation of precipitation and temperature simulation performance of the CMIP3 and CMIP5 historical experiments", Koutroulis et al. 2016).

*Line 138: Maybe also cite any of the interfaces you used, like RStan*: http://mc-stan.org/users/citations/

### 2017-12-09 manuscript/reviewer_reply.Rmd

*Line 141-143: I think the paper thus far is pretty clear. I was hoping to see a few equations here – it helps me especially when components start to become hierarchical!*

>We have added the equations and Stan code as a supplemental file.

*Line 163-164: again, I think equations could really help here to describe the baseline models. I think it’s also important to use these to clarify key details – for example, by training models on a site-by-site basis, you’re estimating separate parameters by site. For example with the uncorrelated noise model, you’re estimating unique variances by site right? Maybe say something like this, in addition to including equations.*

>We now clarify this, using an equation for each baseline model. In particular, we identify
which parameters are estimated on a site-by-site basis and which ones are constant across
all sites, as suggested.

### 2017-12-09 manuscript/draft.Rmd
more baseline eqn stuf

Predictions from the "average" model are centered on the average richness
observed during training, and the confidence intervals are narrow and
constant-width.

The second baseline, called the "naive" model [@hyndman2014], was a simple
autoregressive process with a single year of history:

$$y_t = y_{t-1} + \epsilon_t$$

In contrast to the "average" model, whose predictions were based on the average
richness across the whole time series, the "naive" model predicts that future
observations will be similar to the *final* observed value (e.g., in our
hindcasts the value observed in `r timeframe$last_train_year`), and the
confidence intervals expand rapidly as the predictions extend farther into the
future. Both models' richness predictions are centered on a constant value, so
neither model can anticipate any trends in richness or any responses to future
environmental changes.

>>>>

Predictions from the "average" model are thus centered on $\mu$, which could
either be the mean of the raw training richness values, or an output from the
observer model.  This model's confidence intervals have a constant width that
depends on the standard deviation of $\epsilon$, which can either be the
standard deviation of the raw training richness values, or
$\sigma^\mathrm{residual}$ from the observer model; see supplement).

The second baseline, called the "naive" model [@hyndman2014], was a simple
autoregressive process with a single year of history, i.e. an ARIMA(0,1,0)
model:

$$y_t = y_{t-1} + \epsilon_t,$$

where the standard deviation of $\epsilon$ is a free parameter for each site. In
contrast to the "average" model, whose predictions were based on the average
richness across the whole time series, the "naive" model predicts that future
observations will be similar to the *final* observed value (e.g., in our
hindcasts the value observed in `r timeframe$last_train_year`). Moreover,
because the $\epsilon$ values accumulate over time, the confidence intervals
expand rapidly as the predictions extend farther into the future. Despite these
differences, both models' richness predictions are centered on a constant value,
so neither model can anticipate any trends in richness or any responses to
future environmental changes.
